08-prediction

### 2018-07-31 02_scripts/035-all-plots-modeling.Rmd
scripts

```{r}
# 5h 30 min
var_imp = generateFeatureImportanceData(task, learner = lrn_xgboost, 
                                        measure = rmse, nmc = 2)
saveRDS(var_imp, "/data/patrick/mod/hyperspectral/variable-importance/bf2_ncm2.rda")

@@

imp.xgb$res %>% 
  arrange(desc(feat.imp)) %>% 
  slice(1:30) %>% 
  ggdotchart(x = "index", y = "feat.imp",                              # Color by groups
             sorting = "asc",                       # Sort value in descending order
             add = "segments",                             # Add segments from y = 0 to dots
             #color = "index",
             palette = "nejm",
             #position = position_dodge(1),
             group = "index",
             #title = .y,
             rotate = T,                                # Rotate vertically
             dot.size = 0.5,                                 # Large dot size
             ggtheme = theme_pubr(base_size = 6, margin = F,
                                  legend = "none")) + 
  labs(y = "Score", color = "Spectral region")
```
```{r}
ggsave(here::here("03_figures/results/var-imp-xgboost.png"), height = 3,
       width = 5)
```

>>>>

```{r}
m = readRDS("/data/patrick/mod/hyperspectral/prediction/xgboost_trained_tuned.rda")
# 5h 30 min
var_imp = generateFeatureImportanceData(task, learner = lrn_xgboost, 
                                        measure = rmse, nmc = 50)
saveRDS(var_imp, "/data/patrick/mod/hyperspectral/variable-importance/bf2_ncm50rda")

@@

imp.xgb$res %>% 
  arrange(desc(feat.imp)) %>% 
  slice(1:30) %>% 
  ggdotchart(x = "index", y = "feat.imp",                              # Color by groups
             sorting = "asc",                       # Sort value in descending order
             add = "segments",                             # Add segments from y = 0 to dots
             #color = "index",
             palette = "nejm",
             #position = position_dodge(1),
             group = "index",
             #title = .y,
             rotate = T,                                # Rotate vertically
             dot.size = 0.5,                                 # Large dot size
             ggtheme = theme_pubr(base_size = 6, margin = F,
                                  legend = "none")) + 
  labs(y = "Score", color = "Spectral region")
```

```{r}
ggsave(here::here("03_figures/results/var-imp-xgboost.png"), height = 3,
       width = 5)
```

### 2018-07-31 02_scripts/04_plot_characteristics.Rmd
scripts

@@

```{r}
df <- tibble(
  plot = factor(c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")),
  rmse = c(mean(results_reps$laukiz1), mean(results_reps$laukiz2), mean(results_reps$luiando), mean(results_reps$oiartzun)),
  point_dens = dist_plots,
  mean_defol = mean_defol,
  cov_defol = cov_defol,
  sd_skewness = sd_skewness_defol
)
```

@@

@@

```{r}
prow = plot_grid(rmse_dens, rmse_defol_cov, rmse_defol_cov_sk,  align = 'vh', nrow = 1)
plots_grid <- plot_grid(prow, legend, rel_widths = c(3, .3))
```

```{r}
plots_grid <- plot_grid(rmse_dens, legend, rmse_defol, ncol = 3, rel_widths = c(1, .3, 1))
```

```{r}
save_plot(here("03_figures/results/plot-characteristics.png"), plots_grid, ncol = 4)
```

>>>>

all_plots = readRDS("/data/patrick/mod/hyperspectral/spcv/all_plots_xgboost_blocking.rda")

@@

```{r}
df <- tibble(
  plot = factor(c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")),
  rmse = c(mean(results_reps$laukiz1$rmse), mean(results_reps$laukiz2$rmse), mean(results_reps$luiando$rmse), mean(results_reps$oiartzun$rmse)),
  point_dens = dist_plots,
  mean_defol = mean_defol,
  cov_defol = cov_defol,
  sd_skewness = sd_skewness_defol
)
```

@@

## Differences between models (single vs super)

```{r}
# laukiz1
all_plots$measures.test$rmse[3] - mean(results_reps$laukiz1$rmse)

# laukiz2
all_plots$measures.test$rmse[4] - mean(results_reps$laukiz2$rmse)

# luiando
all_plots$measures.test$rmse[2] - mean(results_reps$luiando$rmse)

# oiartzun
all_plots$measures.test$rmse[1] - mean(results_reps$oiartzun$rmse)
```

@@

```{r}
prow = plot_grid(rmse_dens, rmse_defol_cov,  align = 'vh', nrow = 1)
plots_grid <- plot_grid(prow, legend, rel_widths = c(2, .5))
```

```{r}
#plots_grid <- plot_grid(rmse_dens, legend, rmse_defol, ncol = 3, rel_widths = c(1, .3, 1))
```

```{r}
save_plot(here("03_figures/results/plot-characteristics.png"), plots_grid, ncol = 3)
```

### 2018-07-31 02_scripts/08_prediction.Rmd
scripts

```{r, results='hide'}
library(purrr)
library(raster)
library(furrr)
```

@@

# Load NBI

```{r}
files_nbi = list.files("/data/patrick/mod/hyperspectral/narrow-band-indices/", 
                   pattern = ".grd", full.names = TRUE)

nri = map(files_nbi, ~ brick(.))
```

@@

```{r}
plan(multicore, workers = 5)
nri %<>% 
  future_map(~ as(., "SpatialPixelsDataFrame"), .progress = TRUE) %>% 
  future_map(~ st_as_sf(.), .progress = TRUE)
```

>>>>

```{r, results='hide'}
library(purrr)
library(raster)
library(furrr)
library(sf)
library(pbmcapply)
```

@@

# Load NRI

```{r}
files_nri = list.files("/data/patrick/mod/hyperspectral/narrow-band-indices/", 
                   pattern = ".grd", full.names = TRUE)

nri = map(files_nri, ~ brick(.))
```

@@

```{r}
nri %<>% 
  pbmclapply(function(x) as(x, "SpatialPixelsDataFrame"), mc.cores = 2) %>% 
  pbmclapply(function(x) st_as_sf(x), mc.cores = 2)
```
